Exploiting the Graph: Increasing Engagement in Collaborative Interactive Evolution

### 2017-01-24 2017-CEC-Graph-Based-Population-For- IEC/paper.tex
More related work

In all these systems, the evolutionary interactive process is captured by the system. The genetic lineage of each
individual is presented where users can visualize the relationships between them and evolutionary operators used in
their creation. Also there is information regarding users and their collaborations.  Common offerings show 
interesting individuals order by categories, number of votes, best of the week among others.
These features have the goal of encouraging participation but require the use of a database system 
for their implementation. Picbreeder \cite{picbreeder} is implemented with a service oriented
architecture using a relational database and the file system for genotypes and images.

Other works employ the use of No SQL databases, the work of Seyama and Munetomo \cite{seyama2016development}
employs in their implementation a Platform as-a Service (PaaS) and NoSQL database to facilitate collaboration 
among a large number of users for the interactive modelling of 3D glasess.  This system reduces the user fatigue
by using a collaborative filtering algorithm to show the information searched for and utilized by similar users.

Collaborative IEC systems need to store highly connected data, as it is common in current applications
like social networks, and the world wide web. In order to deal with large datasets of connected data,
graph databases \cite{angles2012comparison} have been proposed as an alternative to relational databases 
which have performance limitations when dealing with highly connected data \cite{holzschuher2013performance}.

The present work builds on a previous proposals and extends the C-IEA approach.
First, it proposes a graph data model for representing the interactive process of C-IEC systems.
Second, it incorporates the graph model to the evolutionary algorithm.
Finally, uses the same model to increase the collaboration of volunteers.

>>>>

In all these systems, the evolutionary interactive process is captured by the system. The genetic lineage of each
individual is presented where users can visualize the relationships between them and evolutionary operators used in
their creation. Also there is information regarding users and their collaborations.  Common offerings show 
interesting individuals order by categories, number of votes, best of the week among others. In a recent work by
Wagy \& Bongard \cite{wagy2014collective} user interaction is needed for evaluating the fitness and developing
new designs of robot locomotiom. Collaboration is encoureged by gamifying the system, using the maximum distance indicator
to inspire the user to try and “beat” previous designs.

Implementing recommendation algorithms or adding gamification techniques have the goal of encouraging participation 
but require the use of a database system for managing the additional data required. 
For example Picbreeder \cite{picbreeder} is implemented with a service oriented
architecture using a relational database and the file system for genotypes and images. Other works employ the 
use of No SQL databases like the work of Seyama and Munetomo \cite{seyama2016development} where they
employ a Platform as-a Service (PaaS) and NoSQL database to facilitate the collaboration 
among a large number of users for the interactive modelling of 3D glasess.  This system reduces the user fatigue
by using a collaborative filtering algorithm to show only the information utilized by similar users.

Collaborative IEC systems need to store highly connected data, as it is common in current applications
like social networks. In order to deal with large datasets of connected data found in these systems,
graph databases \cite{angles2012comparison} have been proposed as an alternative to relational databases 
which have performance limitations when dealing with highly connected data \cite{holzschuher2013performance}.
In this work the use of a graph data model for representing the interactive process of C-IEC systems is proposed.
Moreover, an proof-of-concept implemantation of IEC incorporating the graph model to the evolutionary algorithm is presented.
%Finally, a comparasion of between three deployments of the system, with different increase the collaboration of volunteers.
